Kernel plays a central role in the successes of kernel-based techniques and applications. Conventional kernel-based techniques often adopt some single parametric kernel where the kernel parameters are usually fixed by some heuristic approach. The conventional single  parametric kernels with fixed parameters limit their capacity of the subsequent kernel-based techniques when fitting complex data in a real-world application. Thus, the goal of this thesis is to address the open research challenge of learning effective kernels for real-world applications. The main contribution of this thesis is to investigate novel and effective kernel learning methods for improving the performance of kernel-based techniques towards real applications. The details of our contributions are summarized as follows.
	
First of all, to address the limitation of conventional parametric kernel methods, we first present a family of simple non-parametric kernel learning algorithms (SimpleNPKL), which are able to learn non-parametric kernels from side information by solving a special kind of Semi-Definite Programs (SDP) in a fairly efficient way. We apply SimpleNPKL to several applications, including clustering, classification, and data embedding, and conducted extensive experiments on publicly available data sets to validate the effectiveness and efficiency of our techniques.

Besides, this thesis also explores two new directions of kernel learning in learning effective kernels from data. The first technique is the deep multiple kernel learning, which is inspired by recent developments in deep learning architectures and multiple kernel learning. The second technique is the unsupervised multiple kernel learning, which learns kernels from the data in an unsupervised manner and can be used as a useful tool for data pre-processing. Our  experiments on publicly available data sets show that the two new directions are promising.

Finally, we also investigate the applications of kernel learning techniques to some real-world problems. In particular, the first application is to apply the non-parametric kernel learning techniques for image re-ranking in a social image retrieval task. The second application is to explore the applications of kernel learning for social strength modelling in a social media application. Our extensive empirical studies on large real data further validate the effectiveness of kernel learning techniques in solving real-world applications.



