First, I would like to thank my supervisor Dr Steven C.H. Hoi, who is probably the best supervisor in Nanyang Technological University. Dr. Hoi brought me to the world of machine learning three years ago and worked closely with me for all my published research papers. During my PhD career, he not only inspires me on innovative research ideas with his profound knowledge and amazing wisdom, but also encourages me for being a decent and successful person.

Second, I would like to thank my non-official co-supervisor Dr. Ivor W.H. Tsang, who is one of the most descent researchers in the related areas. The discussion with Dr. Tsang would be the most memorable moments during my research career. Many of the ideas in our collaborated work were generated from our fruitful discussions.

Third, I would like to thank my old friends, especially Min Wu, Juyong Zhang, Zheng Li, Molly Zhou, Sasa Hu and Xiaoxiao Li. You guys shed light into my life. I always cherish the time of eating crabs and drinking beer with Juyong and Min. I thank Molly and Sasa. With you two women of different roles, I never feel lonely. I thank Xiaoxiao Li, as the blue side of life is indispensable and valuable. I sincerely wish you guys would accompany with me in the rest of my life.

I thank the relatively new friends, Linhong Zhu, Shuguo Han, Peilin Zhao, Hao Xia, Pengcheng Wu, Shumo Chu, and Bin Li. I really enjoy the time spent with everyone of you. You guys bring energy to our lab. I thank the friends known in Singapore, Sophia Wan, Louise Huang, Joyce Jia etc. The time with you always flies so quick. I believe we can meet frequently in the future. I thank my mentors in Microsoft Research Asia: Tao Mei, Xian-sheng Hua, Ying-qing Xu, and Shipeng Li. Without the discussions with you, I cannot work out the fruitful publications there. I also thank the great friends made in MSRA: Mingyan Gao, Jialei Wang, Binxing Jiao, Ju Sun, Zhaoyan Ming, and Qiong Wu.

At last, I would like to thank my parents. No matter when I am frustrated, you are always there with me. I pray that you both are healthy and happy forever. I love you.
