{\bf Publication List}:


\begin{itemize}
  \item Jinfeng Zhuang, Jialei Wang, and Steven C.H. Hoi (2011). Unsupervised Multiple Kernel Learning. {\em ACML (submitted)}.
  \item Jinfeng Zhuang, Tao Mei, Steven C.H. Hoi, Xian-sheng Hua, and Shipeng Li (2012). Flickr Community Discovery by Low-Rank Matrix Recovery. {\em WSDM (submitted)}.
  \item Jinfeng Zhuang, Tao Mei, Steven C.H. Hoi, Yingqing Xu, and Shipeng Li (2011). When Recommendation Meets Mobile: Contextual and Personalized Recommendation On The Go. {\em UbiComp}.
  \item Jinfeng Zhuang, Tao Mei, Steven C.H. Hoi, and Xian-sheng Hua (2011). Social Strength Modeling of Flickr Users. {\em ACM Multimedia}.
  \item Jinfeng Zhuang, Ivor W. Tsang, and Steven C.H. Hoi (2011). Two-layer Multiple Kernel Learning. {\em AISTATS}.
  \item Jinfeng Zhuang, Ivor W. Tsang, and Steven C.H. Hoi (2011). A Family of Simple Non-Parametric Kernel Learning from Pairwise Constraints. {\em JMLR}.
  \item Jinfeng Zhuang, Steven C.H. Hoi (2011). A Two-view Model-free Learning Approach for Social Tag Ranking. {\em WSDM}.
  \item Jinfeng Zhuang, and Steven C.H. Hoi (2011). Social Image Tag Ranking by Two-view Learning. Book chapter in {\em Social Media Modeling and Computing}.
  \item Jinfeng Zhuang, Steven C.H. Hoi (2010). Nonparametric Kernel Ranking Approach for Social Image Retrieval. {\em CIVR}.
  \item Jinfeng Zhuang, Steven C.H. Hoi, Aixin Sun, Rong Jin (2010). Entry Selection Techniques for Blog Profiling and Classification. {\em Information Science}. (In Revision)
  \item Jinfeng Zhuang, Ivor W. Tsang, Steven C.H. Hoi (2009). SimpleNPKL : Simple Non-Parametric Kernel Learning. {\em ICML}.
  \item Jinfeng Zhuang, Steven C. H. Hoi, Aixin Sun, Rong Jin (2008). Representative entry selection for profiling blogs. {\em CIKM}.
  \item Jinfeng Zhuang, Steven C. H. Hoi, Aixin Sun (2008). On profiling blogs with representative entries. {\em 2nd Workshop on Analytics for Noisy Unstructured Text Data}.
\end{itemize}

